Copyright

### 2025-01-27 copyright.qmd
Only load video on demand

```{=html}
<div style="position: relative; width: 100%; aspect-ratio: 16 / 9;">
  <iframe src="https://av.tib.eu/player/53550" allowfullscreen style="position: absolute; top: 0; left: 0; width: 100%; height: 100%;"></iframe>
</div>
```
:::

>>>>

The following video "The correct indication of a license" embedded from the TIB AV-Portal ([Data Privacy Statement](https://av.tib.eu/privacy)) explains the correct attribution of Creative Commons licenses.

```{=html}
<details>
  <summary>Load video</summary>
  <div style="position: relative; width: 100%; aspect-ratio: 16 / 9;">
    <iframe loading="lazy" src="https://av.tib.eu/player/53550" allowfullscreen style="position: absolute; top: 0; left: 0; width: 100%; height: 100%;"></iframe>
  </div>
</details>
```
:::
